sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-03 doc/paper.Rmd
Tweak timing fig

```{r timing, fig.cap="(ref:timing-fig)", out.width="3.5in", fig.align='center'}
f <- here::here("figs", "timing2-logx-PE.pdf")
if (!file.exists(f)) {
  download.file("https://www.dropbox.com/s/3aco85mizuplz7z/timing2-logx.pdf?dl=1", 
    destfile = f)
}
knitr::include_graphics(f)
```

>>>>

```{r timing, fig.cap="(ref:timing-fig)", out.width="3.5in", fig.align='center'}
f <- here::here("figs", "timing-spatial.pdf")
knitr::include_graphics(f)
```
